\documentclass[11pt]{article}

\usepackage{multicol}
\usepackage{times}
\usepackage{graphicx}
\usepackage{epsfig}

\textheight 9in
\textwidth 6.5in
\oddsidemargin 0in
\evensidemargin 0in
\topmargin -.5in
\pagestyle{empty}
\newcommand{\setspace}[1]{\renewcommand{\baselinestretch}{#1}\large\normalsize}
\setspace{1.1}
\renewcommand{\textfraction}{0.1}
\renewcommand{\topfraction}{0.9}
\newcommand{\tods}{{\em TODS\/}}

\begin{document}
\begin{center}
{\Large\bf Developments at ACM {\em TODS}}\\[2ex]
{\large\it  Richard Snodgrass}\\[1ex]
{\tt rts@cs.arizona.edu}\\[3ex]
\end{center}

The June 2004 issue of \tods\ is another blockbuster, with five papers
in this issue. In fact, the first two issues of 2004 contain the same number
of papers as appeared in all of 2002. While the Web is still really
hot, with papers on evaluating top-$k$ queries over the Web, XML indexing,
and dynamically generated web content, this issue also has papers with
innovative approaches to bulk loading and to sequence queries. And to get a head
start on the September issue, check out the Upcoming Issues page ({\tt http://www.acm.org/tods/Upcoming.html}).

\vspace{2em}
I have appointed four new Associate Editors.

\begin{itemize}
\item {\bf Luis Gravano} works at the juncture of databases and information
  retrieval, including research on distributed search over text
  databases, Web search, information extraction, and text mining.

\item {\bf Ralf Hartmut G\"{u}ting} works on extensible and modular database
system architectures, and in spatial and spatio-temporal data modeling and 
implementation issues, especially in the recent flavor of ``moving 
objects databases''.

\item {\bf Hank Korth}'s most recent publications have been in the areas of
XML-relational data integration and main-memory databases.  He is currently
addressing CPU-architecture aware query processing and also data modeling
and query processing issues arising from homeland-security applications.

\item {\bf Betty Salzberg} does research on database kernel issues, in
  particular spatial and temporal indexing, online reorganization, and
  concurrency and recovery.

\end{itemize}

\noindent
All four are internationally-known scholars in the field of
database systems and are well known also to the database community
through their past service. I'm gratified that they are willing
to help \tods\ continue to improve.

\end{document}
