\documentclass{article}[11pt]

\usepackage{multicol}
\usepackage{times}
\usepackage{graphicx}

\textheight 9in
\textwidth 6.5in
\oddsidemargin 0in
\evensidemargin 0in
\topmargin -.5in
\pagestyle{empty}
\newcommand{\setspace}[1]{\renewcommand{\baselinestretch}{#1}\large\normalsize}
\setspace{1.2}
\renewcommand{\textfraction}{0.1}
\renewcommand{\topfraction}{0.9}
\newcommand{\tods}{{\em TODS\/}}

\begin{document}
\begin{center}
{\Large\bf Changes to the {\em TODS} Editorial Board}\\[2ex]
{\large\it  Richard Snodgrass}\\[1ex]
{\tt rts@cs.arizona.edu}\\[3ex]
\end{center}

The December issue should be out soon, if it isn't already. It is a special
issue of papers invited from the SIGMOD'04 and PODS'04 conferences. I thank
the authors, associate editors, and reviewers (some from the SIGMOD and PODS
program committees) for writing, reviewing, revising, reviewing again, and
then getting into final form these papers in the amazingly short time of
eighteen months. This is a very nice issue, with seven substantive papers.

The 2005 volume (volume 30) of {\em TODS} is the largest one yet, by far,
and the first one over 1000 pages (over 1100 pages, actually). Included in
this volume, in the September 2005 issue, is one of Alberto Mendelzon's last
papers, ``Capturing summarizability with integrity constraints in OLAP.''
Alberto was a {\em TODS} Associate Editor for four years, and before that
worked with me as SIGMOD Information Director. I greatly miss him and his
gentle smile.

Submissions to {\em TODS} have doubled over the past three years. I'm very
pleased to announce the appointment of four new Associate Editors, bringing
the Editorial Board to 23.\footnote{\tt http://www.acm.org/tods/Editors.html}

\begin{description}
\item[Phokion Kolaitis] works on logic in databases. Current research 
interests
include data integration and interoperability, metadata management, query 
languages, and deductive databases.

\item[Ken Ross's] current interests include query processing and optimization,
particularly in the context of database systems running on new
and/or nontraditional hardware.  He also has projects in several
application domains, including archeology, architecture, and biology.

\item[Pierangela Samarati's] research interests are in the areas of access
control policies, models, languages, and systems; data security and privacy;
information system security; and information protection in general.

\item[S.~Sudarshan's] main research interests include query optimization, 
keyword queries on structured and semi-structured data, and 
fine-grained access control.  He is also working on tools for
supporting database application development. 
\end{description}

\noindent
We're very fortunate that such accomplished scholars are willing to invest
their valuable time to handle manuscripts.
\end{document}
